Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-03 grove-paper.tex
Get graphviz to play nice with latexmk

%% Packages
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage[pdf]{graphviz}

@@

\begin{figure}
\centering
\digraph[]{simple-tree-with-hole}{
  node [shape=Mrecord,fontsize=11,ranksep=0];
  edge [arrowhead=vee,fontsize=11,weight=2];
  rankdir = LR;
  {rank=min; n0 [shape=point]};
  n0 [label="{0: Root_root|{<root> root}}",style=filled,fillcolor=black];
  n3 [label="{3: Exp_plus|{<left> left|<right> right}}",style=filled,fillcolor=white];
  n6 [label="{6: Exp_num(2)|{}}",style=filled,fillcolor="#ddffdd"];
  n3:left -> n6 [color=black,label="7",edgeURL="#",edgetooltip="id: 7\nsource: 3\nindex: Lang.Index.Exp_plus_left\ntarget: 6",labeltooltip="id: 7\nsource: 3\nindex: Lang.Index.Exp_plus_left\ntarget: 6"];
  n0:root -> n3 [color=black,label="4",edgeURL="#",edgetooltip="id: 4\nsource: 0\nindex: Lang.Index.Root_root_root\ntarget: 3",labeltooltip="id: 4\nsource: 0\nindex: Lang.Index.Root_root_root\ntarget: 3"]}
\begin{tikzpicture}
% TODO: texttt
% TODO: position the different graphs
\path (0cm,0cm) graph[tree layout] {
  + -> {
    2[as={\texttt{2}}],
    % <empty>
  }
};
\end{tikzpicture}
\caption{Scenario X: Holes in the Tree}
\label{fig:Scenario X: Holes in the Tree}
\end{figure}

>>>>

%% Packages
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{graphicx}

% Support \includegraphics of .dot files
\DeclareGraphicsRule{.dot}{pdf}{.pdf}{`dot -Tpdf #1 -o \noexpand\OutputFile}

@@

\begin{figure}
\centering 
\includegraphics{simpletreewithholeX.dot}
%\digraph[]{simpletreewithholeX}{
%  node [shape=Mrecord,fontsize=11,ranksep=0];
%  edge [arrowhead=vee,fontsize=11,weight=2];
%  rankdir = LR;
%  {rank=min; n0 [shape=point]};
%  n0 [label="{0: Root_root|{<root> root}}",style=filled,fillcolor=black];
%  n3 [label="{3: Exp_plus|{<left> left|<right> right}}",style=filled,fillcolor=white];
%  n6 [label="{6: Exp_num(2)|{}}",style=filled,fillcolor="#ddffdd"];
%  n3:left -> n6 [color=black,label="7",edgeURL="#"];
%  n0:root -> n3 [color=black,label="4",edgeURL="#"]}
\begin{tikzpicture}
% TODO: texttt
% TODO: position the different graphs
\path (0cm,0cm) graph[tree layout] {
  + -> {
    2[as={\texttt{2}}],
    % <empty>
  }
};
\end{tikzpicture}
\caption{Scenario X: Holes in the Tree}
\label{fig:Scenario X: Holes in the Tree}
\end{figure}
